---
title: "p8105_hw5_rk3445"
author: "Rosie Kwon"
date: "2025-11-01"
output: html_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

A function that checks whether there are duplicate birthdays in the group
```{r}
duplicate_birthday <- function(n, num_days = 365) {
  birthdays <- sample(0:(num_days - 1), n, replace = TRUE)
  if (length(birthdays) != length(unique(birthdays))) {
    return(TRUE)   
  } else {
    return(FALSE)  
  }
}
```

Next, run this function 10000 times for each group size between 2 and 50. For each group size, compute the probability that at least two people in the group will share a birthday by averaging across the 10000 simulation runs. Make a plot showing the probability as a function of group size, and comment on your results.

